%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Classicthesis-Styled CV
% LaTeX Template
% Version 1.0 (22/2/13)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% Alessandro Plasmati
%
% License:
% CC BY-NC-SA 3.0 (http://creativecommons.org/licenses/by-nc-sa/3.0/)
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass{scrartcl}

\reversemarginpar % Move the margin to the left of the page 

\newcommand{\MarginText}[1]{\marginpar{\raggedleft\itshape\small#1}} % New command defining the margin text style

\usepackage[nochapters]{classicthesis} % Use the classicthesis style for the style of the document
\usepackage[LabelsAligned]{currvita} % Use the currvita style for the layout of the document

\renewcommand{\cvheadingfont}{\LARGE\color{Maroon}} % Font color of your name at the top

\usepackage{hyperref} % Required for adding links	and customizing them
\hypersetup{colorlinks, breaklinks, urlcolor=Maroon, linkcolor=Maroon} % Set link colors

\newlength{\datebox}\settowidth{\datebox}{Spring 2011} % Set the width of the date box in each block

\newcommand{\NewEntry}[3]{\noindent\hangindent=2em\hangafter=0 \parbox{\datebox}{\small \textit{#1}}\hspace{0em} #2 #3 % Define a command for each new block - change spacing and font sizes here: #1 is the left margin, #2 is the italic date field and #3 is the position/employer/location field
\vspace{0.5em}} % Add some white space after each new entry

\newcommand{\Description}[1]{\hangindent=2em\hangafter=0\noindent\raggedright\footnotesize{#1}\par\normalsize\vspace{1em}} % Define a command for descriptions of each entry - change spacing and font sizes here

%----------------------------------------------------------------------------------------
% My custom changes 
%----------------------------------------------------------------------------------------

% Remove page numbers 
\pagenumbering{gobble}

% Fix margins? 
\usepackage[left=1.5in,right=1in,top=1in,bottom=1in]{geometry}

%----------------------------------------------------------------------------------------

\begin{document}

\thispagestyle{empty} % Stop the page count at the bottom of the first page

%----------------------------------------------------------------------------------------
%	NAME AND CONTACT INFORMATION SECTION
%----------------------------------------------------------------------------------------

\begin{cv}{\spacedallcaps{Mihailo Isakov}}\vspace{1.5em} % Your name

\noindent\spacedlowsmallcaps{Personal Information}\vspace{0.5em} % Personal information heading

%\NewEntry{}{\textit{Born in Serbia,}}{3 October 1992} % Birthplace and date

\NewEntry{email}{\href{mailto:mihailo@tamu.edu}{mihailo@tamu.edu}} % Email address

\NewEntry{website}{\href{https://ascslab.org/members/mihailo/index.html}{https://ascslab.org/members/mihailo/index.html}} % Personal website

\NewEntry{phone}{+1 541 780 3005} % Phone number(s)

\vspace{1em} % Extra white space between the personal information section and goal

\noindent\spacedlowsmallcaps{Research Interests}\vspace{1em} % Goal heading, could be used for a quotation or short profile instead

\Description{Intersection of computer architecture, machine learning, high performance computing, and security with a particular emphasis on: hardware and ML algorithm co-design, HPC I/O throughput modelling, secure execution of machine learning models, hardware acceleration of deep neural network (DNN) training, edge-deployed, low power, and low latency DNN training.}\vspace{0em} % Goal text

%----------------------------------------------------------------------------------------
%	EDUCATION
%----------------------------------------------------------------------------------------

\spacedlowsmallcaps{Education}\vspace{0.5em}

%\NewEntry{2016-2022}{Ph.D., Electrical and Computer Engineering}
\hspace{2em}Ph.D., Electrical and Computer Engineering

\Description{\MarginText{2020--2022}\textbf{Texas A\&M University, College Station, TX}\newline
Advisor: Prof.~Michel A. Kinsy
}

%------------------------------------------------


%\NewEntry{2016-2022}{Ph.D., Electrical and Computer Engineering}
\hspace{2em}Ph.D., Electrical and Computer Engineering

\Description{\MarginText{2016--2020}\textbf{Boston University, Boston, MA}\newline
Advisor: Prof.~Michel A. Kinsy\newline
Laboratory transferred to Texas A\&M University in September 2020.
}

%------------------------------------------------

%\NewEntry{2015-2016}{Masters in Software Engineering}
\hspace{2em}Masters in Software Engineering

\Description{\MarginText{2015--2016}\textbf{University of Novi Sad, Novi Sad, Serbia}\newline
Transferred in second year to the Boston University's Doctoral Program. \newline\newline}
\vspace{-2em}

%------------------------------------------------

%\NewEntry{2011-2015}{Bachelor in Electrical Engineering}
\hspace{2em}Bachelor in Electrical Engineering

\Description{\MarginText{2011--2015}\textit{Software Engineering Specialization} \newline
\textbf{University of Novi Sad, Novi Sad, Serbia}\newline
Undergraduate Thesis Title: Inertial Motion Capture System Body Pose Reconstruction using Machine Learning.}

%------------------------------------------------

%----------------------------------------------------------------------------------------
%	WORK EXPERIENCE
%----------------------------------------------------------------------------------------

\noindent\spacedlowsmallcaps{Work Experience}\vspace{0.5em}

%------------------------------------------------

%\NewEntry{2015--2016}{Freelance Researcher}
Freelance Researcher\newline
\Description{\MarginText{2015--2016}\textbf{Machine learning and data science}\newline
    Worked as a freelance researcher for several machine learning startups.\newline
}
\vspace{-1em}

%------------------------------------------------

%\NewEntry{2015--2016}{Teaching Assistant}
\hspace{2em}Teaching Assistant

\Description{\MarginText{2015--2016}\textbf{University of Novi Sad, Novi Sad, Serbia}\newline
    Prepared and taught labs for the (1) artificial intelligence and (2) soft computing classes.\newline
}
\vspace{-1em}

%------------------------------------------------

%\NewEntry{Jul--Sep 2014}{Research intern --- Enschede, Netherlands}
\hspace{2em}Research intern 

\Description{\MarginText{Jul--Sep 2014}\textbf{Xsens Technologies B.V. Enschede, Netherlands}\newline
    Researched efficient implementations of a human pose reconstruction algorithm from a limited
number of inertial motion capture sensors worn on the body.\newline
}
\vspace{-1em}

%------------------------------------------------

%\NewEntry{2013--2014}{Co-founder / CTO --- Novi Sad, Serbia}
\hspace{2em}Co-founder / CTO

\Description{\MarginText{2013--2014}\textbf{Citrus Tech Design}\newline
    Co-founded startup building smart skateboards, longboards and snowboards.\newline
Product video: \href{https://drive.google.com/file/d/0B-JezYn4rPEyZE1NQzM4TUVvYzQ/view?usp=sharing}{LightBoard}}
\vspace{-1em}

%------------------------------------------------



\newpage

%----------------------------------------------------------------------------------------
%	CONFERENCE PUBLICATIONS
%----------------------------------------------------------------------------------------

\normalsize
\spacedlowsmallcaps{Conference publications}\vspace{1em}

\footnotesize{
\begin{enumerate}


    \item \textbf{M. Isakov}, E. del Rosario, S. Madireddy, P. Balaprakash, P. Carns, R. B. Ross, M. A. Kinsy, "HPC I/O Throughput Bottleneck Analysis with Explainable Local Models," in 2020 SC20: International Conference for High Performance Computing, Networking, Storage and Analysis (SC), Atlanta, GA, US, 2020 pp. 1-13.

    \item \textbf{M. Isakov}, E. del Rosario, S. Madireddy, P. Balaprakash, P. Carns, R. B. Ross, M. A. Kinsy, "Toward Generalizable Models of I/O Throughput," 2020 IEEE/ACM International Workshop on Runtime and Operating Systems for Supercomputers (ROSS), GA, USA, 2020, pp. 41-49.

    \item E. del Rosario, M. Currier, \textbf{M. Isakov}, S. Madireddy, P. Balaprakash, P. Carns, R. B. Ross, M. A. Kinsy, "Gauge: An Interactive Data-Driven Visualization Tool for HPC Application I/O Performance Analysis," 2020 IEEE/ACM Fifth International Parallel Data Systems Workshop (PDSW), GA, USA, 2020, pp. 15-21.

    \item V. Gadepally, \textbf{M. Isakov}, R. Agrawal, J. Kepner, K. Gettings and M. A. Kinsy, "Homomorphic Encryption Based Secure Sensor Data Processing," 2020 IEEE High Performance Extreme Computing Conference (HPEC), Waltham, MA, USA, 2020, pp. 1-7.

    \item \textbf{M. Isakov}, V. Gadepally, K. M. Gettings and M. A. Kinsy, "Survey of Attacks and Defenses on Edge-Deployed Neural Networks," IEEE High Performance Extreme Computing Conference (\textbf{HPEC}), Waltham, MA, USA, 2019, pp. 1-8. \textbf{Best Student Paper Nominee}.

    \item \textbf{M. Isakov}, L. Bu, H. Cheng, and M. A. Kinsy: “Preventing Neural Network Model Exfiltration in Machine Learning Hardware Accelerators”. In the 2018 Asian Hardware Oriented Security and Trust Symposium (\textbf{AsianHOST}), 2018.

    \item \textbf{M. Isakov} and M. A. Kinsy: “NoSync: Particle Swarm Inspired Distributed DNN Training”. In the 27th International Conference on Artificial Neural Networks (\textbf{ICANN}), 2018.

    \item \textbf{M. Isakov}, A. Ehret and M. Kinsy, "ClosNets: Batchless DNN Training with On-Chip a Priori Sparse Neural Topologies," 28th International Conference on Field Programmable Logic and Applications (\textbf{FPL}), Dublin, 2018, pp. 55-554.

    \item \textbf{M. Isakov}, A. Ehret and M. Kinsy: “Chameleon: A Generalized Reconfigurable Open-Source Architecture for Deep Neural Network Training”. In the 2018 IEEE High Performance Extreme Computing Conference (\textbf{HPEC}), 2018. \textbf{Best student paper nominee}. 

    \item A. Ehret, \textbf{M. Isakov} and M. A. Kinsy: “Towards a Generalized Reconfigurable Agent Based Architecture: Stock Market Simulation Acceleration”, International Conference on Reconfigurable Computing and FPGAs (\textbf{ReConFig}), 2018.

    \item J. R. Doppa, R. G. Kim, \textbf{M. Isakov}, M. A. Kinsy, H. Kwon and T. Krishna: “Adaptive Manycore Architectures for Big Data Computing”. In the International Symposium on Networks-on-Chip (\textbf{NOCS}), October 2017.

    \item H. Hosseinzadeh, \textbf{M. Isakov}, M. Darabi, A. Patooghy, and M. Kinsy: “Janus: An uncertain cache architecture to cope with side channel attacks”. In 2017 IEEE 60th International Midwest Symposium on Circuits and Systems (\textbf{MWSCAS}) Aug 2017. \textbf{The Myril B. Reed Best Paper Award}.

    \item E. Taheri, \textbf{M. Isakov}, A. Patooghy, and M. Kinsy: “Advertiser Elevator: a Fault Tolerant Routing Algorithm for Partially Connected 3D Network-on-Chips”. In 2017 IEEE 60th International Midwest Symposium on Circuits and Systems (\textbf{MWSCAS}) Aug 2017.

    \item M. Kinsy, S. Khadka, \textbf{M. Isakov} and A. Farrukh: “Hermes: Secure Heterogeneous Multicore Architecture Design”. In the IEEE International Symposium on Hardware Oriented Security and Trust (\textbf{HOST}), May 2017.

    \item M. Kinsy, S. Khadka and \textbf{M. Isakov}: “PreNoc: Neural Network based Predictive Routing for Network-on-Chip Architectures”. In the 27th edition of the ACM Great Lakes Symposium on VLSI (\textbf{GLSVLSI}), May 2017.

\end{enumerate}
}

\newpage

%----------------------------------------------------------------------------------------
%	JOURNAL PUBLICATIONS
%----------------------------------------------------------------------------------------

\normalsize
\spacedlowsmallcaps{Journal publications}\vspace{1em}

\footnotesize{
\begin{enumerate}
    \item E. Taheri, \textbf{M. Isakov}, A. Patooghy, M. A. Kinsy: “Addressing a New Class of Reliability Threats in 3-Dimensional Network-on-Chips”. In the Transactions on Computer-Aided Design of Integrated Circuits and Systems (\textbf{TCAD}), 2019.

    \item M. A. Kinsy, L. Bu, \textbf{M. Isakov} and M. Mark: “Designing Secure Heterogeneous Multicore Systems from Untrusted Components”. \textbf{Cryptography}, vol. 2, iss. 3, no. 12, 2018.

    \item L. Bu, \textbf{M. Isakov} and M. A. Kinsy: “RASSS: A Hijack-resistant Confidential Information Management Scheme for Distributed Systems”. In the Institution of Engineering and Technology (\textbf{IET}), - Computers and Digital Techniques, 2018.

    \item L. Bu, \textbf{M. Isakov}, and M. A. Kinsy: “A Secure and Robust Scheme for Sharing Confidential Information in IoT Systems”. In the Elsevier Journal for Ad Hoc Networks, (\textbf{Ad Hoc Networks}), 2018.

\end{enumerate}
}

%----------------------------------------------------------------------------------------
%	WORKSHOP PUBLICATIONS
%----------------------------------------------------------------------------------------

\normalsize
\spacedlowsmallcaps{Workshop publications}\vspace{1em}

\footnotesize{
\begin{enumerate}
    \item \textbf{M. Isakov}, "Secure RISC-V Architectures Design Space Exploration Using the BRISC-V Platform", Workshop on Secure RISC-V Architecture Design (SECRISC-V) 2020, Boston, MA.

    \item N. Boskov, \textbf{M. Isakov} and M. A. Kinsy: “CodeTrolley: Hardware-Assisted Control Flow Obfuscation”. Boston Area Architecture 2019 Workshop (BARC19)

    \item \textbf{M. Isakov} and M. A. Kinsy: “NeuroFabric: A Priori Sparsity for Training on the Edge”. In the 2019 tinyML Summit (tinyML), 2019.

    \item R. Agrawal, S. Bandara, A. Ehret, \textbf{M. Isakov}, M. Mark, and M. A. Kinsy: “The BRISC-V Platform: A Practical Teaching Approach for Computer Architecture”, In Workshop on Computer Architecture Education (WCAE), 2019.

    \item \textbf{M. Isakov} and M. A. Kinsy: “ClosNets: a Priori Sparse Topologies for Faster DNN Training”, Boston Area Architecture 2018 Workshop (BARC18), 2018.

    \item M. A. Kinsy, \textbf{M. Isakov}, A. Ehret and D. Kava: “SAPA: Self-Aware Polymorphic Architecture”, Boston Area Architecture 2018 Workshop (BARC18), 2018.

\end{enumerate}
}

%----------------------------------------------------------------------------------------
%   REPORTS
%----------------------------------------------------------------------------------------

\normalsize
\spacedlowsmallcaps{Reports}\vspace{1em}

\footnotesize{
\begin{enumerate}

     \item \textbf{M. Isakov}, M. Kinsy. "NeuroFabric: Identifying Ideal Topologies for Training A Priori Sparse Networks", Report v1.0, Dec. 2019.
     
    \item N. Boskov, \textbf{M. Isakov}, M. Kinsy. "Drndalo: Lightweight Control Flow Obfuscation Through Minimal Processor/Compiler Co-Design", arXiv preprint arXiv:1912.01560, 2019.
   
    \item P. Ren, M. Kinsy, M. Zhu, S. Khadka, \textbf{M. Isakov}, A. Ramrakhyani, T. Krishna, and N. Zheng. “FASHION: Fault-Aware Self-Healing Intelligent On-chip Network”. arXiv:1702.02313, 2017.

\end{enumerate}
}

%----------------------------------------------------------------------------------------
%   Outreach activities
%----------------------------------------------------------------------------------------
\normalsize
\spacedlowsmallcaps{Outreach Activities}\vspace{1em}

\footnotesize{
\begin{enumerate}
    \item Summer 2019 - Cybersecurity: Introduction to Hardware Security - University of the Virgin Islands Summer Program
    \item Summer 2017 - Summer Challenge: Electrical Engineering - For high school students as part of the Boston University Summer Program.
\end{enumerate}
}


\end{cv}

\end{document}
